Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-10-30 Paper/main.tex
Added paper files
Update paper stuff

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[version=4]{mhchem}
\usepackage{siunitx}
\usepackage{longtable,tabularx}
\setlength\LTleft{0pt}

@@

\author{
  Shreyas Ananthan\footnote{SOME JOB TITLE, AIAA Member},
  Michael J. Brazell\footnote{Researcher III, High-Performance Algorithms and Complex Fluids, AIAA Member},
  Matthew J. Churchfield\footnote{SOME JOB TITLE, AIAA Member}, \\
  Ganesh Vijayakumar\footnote{Researcher III, Mechanical Engineering, AIAA Member}, and
  Shashank Yellapantula\footnote{SOME JOB TITLE, AIAA Member}
}
\affil{National Renewable Energy Laboratory, Golden CO 80401}

@@

\section{Introduction}
\lettrine{P}{ut} the introduction here.

@@

\section{Methodology}
Write something about Nalu-Wind and AMR-Wind.

\section{Results}
Write something about Nalu-Wind and AMR-Wind.

@@

\section*{Acknowledgments}
This research was supported by the Wind Energy Technologies Office of
the US Department of Energy Office of Energy Efficiency and Renewable
Energy.  Sandia National Laboratories is a multimission laboratory
managed and operated by National Technology \& Engineering Solutions
of Sandia, LLC, a wholly owned subsidiary of Honeywell International
Inc., for the U.S. Department of Energy's National Nuclear Security
Administration under contract DE-NA0003525. The views expressed in the
article do not necessarily represent the views of the U.S. Department
of Energy or the United States Government.

>>>>

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[version=4]{mhchem}
\usepackage{siunitx}
\usepackage{longtable,tabularx}
\usepackage{fixme}
\setlength\LTleft{0pt}

% Setup fixme env for collaborative notes
\fxsetup{status=draft, layout=inline, theme=color}

@@

\author{
  Shreyas Ananthan\footnote{SOME JOB TITLE, AIAA Member},
  Michael J. Brazell\footnote{Researcher III, High-Performance Algorithms and Complex Fluids, AIAA Member},
  Ganesh Vijayakumar\footnote{Researcher III, Mechanical Engineering, AIAA Member}, and
  Shashank Yellapantula\footnote{SOME JOB TITLE, AIAA Member}
}
\affil{National Renewable Energy Laboratory, Golden CO 80401}

@@

\section{Introduction}
\fxnote{This is the introduction from the abstract.  Update with real
  introduction.}

\lettrine{P}{ut} the introduction here.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SECTION 2: METHODOLOGY
%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{methodology}

%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SECTION 3: RESULTS
%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{results}

@@

\section*{Acknowledgments}
\fxnote{Acknowledge Matt for work on BC}

This research was supported by the Wind Energy Technologies Office of
the US Department of Energy Office of Energy Efficiency and Renewable
Energy.  Sandia National Laboratories is a multimission laboratory
managed and operated by National Technology \& Engineering Solutions
of Sandia, LLC, a wholly owned subsidiary of Honeywell International
Inc., for the U.S. Department of Energy's National Nuclear Security
Administration under contract DE-NA0003525. The views expressed in the
article do not necessarily represent the views of the U.S. Department
of Energy or the United States Government.

\fxnote{ADD ANY NREL ACKNOWLEDGEMENTS NECESSARY HERE}
